Roster Review (Generic)

### 2019-06-15 rosterReview_generic.Rmd
WIP adding latest data retrieval methods

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  # filter(position %in% c('SP','RP')) %>% 
  View()

>>>>

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  # filter(position %in% c('SP','RP')) %>% 
  filter(grepl("Plouffe",team)) %>% 
  arrange(pos_zar %>% desc) %>% 
  View()
